\section{Application Requirements}
This section presents functional and non-functional requirements for the application, which will be categorized by priority as follows:
\begin{itemize}
   \item (M) Must: Crucial for the system's operation.
   \item (S) Should: Highly recommended, though not mandatory.
   \item (C) Could: Optional for implementation.
\end{itemize}

\subsection{Functional Requirements}
Here is a comprehensive list of all functional requirements for the application.
\subsubsection*{User Management}
For simplicity, we will not implement user registration or logins. The user roles will also be for informational purposes only, as every user will have full access to all functionalities.
\begin{itemize}
   \item Users can create, update, and delete other users (M).
   \item Users are displayed in a table view (M).
   \item Users can set and update the following attributes for a user: name, email, phone number, role, status, bio (M).
   \item Users can be filtered by: their roles (S).
\end{itemize}

\subsubsection*{Task Management}
A similar approach applies to tasks, everyone will be able to manage anyone's tasks.
\begin{itemize}
   \item Users can create, update, and delete tasks (M).
   \item Tasks are displayed on a Kanban board (M). 
   \item Users can set and update the following task attributes: title, status, priority, tag, due date, and description (M).
   \item Users can be linked to tasks as assignees (M).
\end{itemize}

\subsubsection*{Dashboard}
\begin{itemize}
   \item A new users widget are displayed on the dashboard (M).
   \item A new tasks widget are be displayed on the dashboard (M).
   \item The widgets communicate with each other in some way (M).
   \item The dashboard displays a monthly user count graph (C).
   \item The dashboard displays a monthly task completion graph (C).
\end{itemize}

\subsubsection*{Settings}
\begin{itemize}
   \item Users can switch between light and dark themes (C).
   \item Users can switch between Slovak and English languages (C).
\end{itemize}

\subsection{Non-functional Requirements}
Here is a comprehensive list of all non-functional requirements for the application.
\begin{itemize}
   \item The application is divided into several microfrontends (M).
   \item Each microfrontend is isolated from the others to prevent cascading failures (M).
   \item The application is easily scalable by adding new microfrontends (M).
   \item The application is easy to use and intuitive (S).
   \item The microfrontends are easily customizable (S).
\end{itemize}