\section{Requirements}
The requirements for the application are categorized by priority as follows:
\begin{itemize}
   \item (M) Must: Crucial for the system's operation.
   \item (S) Should: Highly recommended, though not mandatory.
   \item (C) Could: Optional for implementation.
\end{itemize}

\subsection{Functional Requirements}
Here is a comprehensive list of all functional requirements for the application.\\\\
\textbf{User Management}
\begin{itemize}
   \item Users can create, update, and delete other users. (M)
   \item Users are displayed in a list view. (M)
   \item Users can set and update the following attributes for a user: name, email, phone number, role, status, bio. (M)
   \item Users can be filtered by: name, email, phone number and role. (S)
\end{itemize}
\textbf{Project Management}
\begin{itemize}
   \item Users can create, update, and delete projects. (M)
   \item Projects are displayed in a list view. (M)
   \item Users can set and update the following project attributes: name, company, status, summary. (M)
   \item Users can be linked to projects as members. (M)
   \item Projects can be filtered by: name, company, status, and members (S)
\end{itemize}
\  \\
\textbf{Task Management}
\begin{itemize}
   \item Users can create, update, and delete tasks. (M)
   \item Tasks are displayed on a Kanban board. (M)
   \item Users can set and update the following task attributes: title, status, tags, due date, priority, and description. (M)
   \item Users can be linked to tasks as assignees. (M)
   \item Users can link tasks to projects. (M)
   \item Tasks can be filtered by: title, project, and assignees. (S)
\end{itemize}
\  \\
\textbf{Dashboard}
\begin{itemize}
   \item User's active, new, and completed project statistics are displayed on the dashboard. (M)
   \item User's active, new, and completed task statistics are displayed on the dashboard. (M)
   \item The dashboard contains widgets for the user's projects and tasks. (M)
   \item The dashboard includes a widget of new users. (M)
   \item The dashboard displays a task completion graph. (C)
\end{itemize}
\textbf{Settings}
\begin{itemize}
   \item Users can switch between light and dark themes. (C)
   \item Users can switch between Slovak and English languages. (C)
\end{itemize}

\subsection{Non-functional Requirements}
Here is a comprehensive list of all non-functional requirements for the application:
\begin{itemize}
   \item The application is divided into several microfrontends. (M)
   \item Each microfrontend is isolated from the others to prevent cascading failures. (M)
\end{itemize}