\chapter{Analysis}
\label{chap:Analysis} 

\section{Introduction to Microfrontends}
\subsection{Background}
Provide an overview of the evolution of web development architectures, emphasizing the challenges associated with monolithic frontend architectures.
\subsection{Definition of Microfrontends}
Define microfrontends and highlight its significance in addressing the limitations of traditional monolithic frontend development.
\subsection{Key Characteristics}
Discuss the essential features and characteristics of microfrontends, such as modularity, independent deployment, and technology agnosticism.

\section{Microservices Architecture}
\subsection{Overview}
Briefly explain the concept of microservices architecture, drawing parallels between microfrontends and microservices.
\subsection{Benefits and Challenges}
Explore the advantages and challenges of microservices architecture, emphasizing how these factors influenced the adoption of microfrontends.

\section{Architecture Patterns}
\subsection{Single Page Application (SPA)}
Discuss the traditional SPA architecture and its limitations that led to the emergence of microfrontends.
\subsection{Module Federation}
Explain the concept of module federation as a key technique in microfrontends, allowing independent development and deployment of frontend modules.
\subsection{Server-Side Includes (SSI)}
Explore server-side includes and how they contribute to the composition of microfrontends, enabling seamless integration of different parts of the application.
\subsection{Frontend Composition Strategies}
Discuss various strategies for composing microfrontends, such as Build-Time Integration, Runtime Integration, and Server-Side Composition, highlighting their pros and cons.

\section{Implementation Technologies}
\subsection{JavaScript Frameworks}
Survey popular JavaScript frameworks (e.g., React, Angular, Vue.js) and their compatibility with microfrontends.
\subsection{Web Components}
Explore the role of web components in microfrontends, discussing how they contribute to the encapsulation and reusability of frontend elements.
\subsection{Communication Protocols}
Examine communication protocols used in microfrontends, such as Custom Events, Pub/Sub, and HTTP APIs.
\section{Case Studies and Examples}
Present case studies of organizations that have successfully adopted microfrontends, highlighting the benefits they achieved.