\chapter{Implementation}
\label{chap:Implementation}
Provide a description outlining the purpose and content of this chapter, detailing the topics being discussed herein.

\section{Overview}
\begin{itemize}
   \item Describe the application implementation process.
   \item Highlight key considerations and the overall approach to implementing micro-frontends.
\end{itemize}

\section{Styling \& Sharing}
\begin{itemize}
   \item Describe the challenge posed by CSS in a micro-fronted architecture, where styles are global, inherit, and cascade without the support of a module system, namespacing, or encapsulation.
   \item Highlight the necessity of ensuring that each micro frontend doesn't conflict with others regarding CSS properties.
   \item Explain the approach taken to address these challenges, emphasizing the need for consistency in the graphical user interface (GUI) across all micro frontends.
   \item Discuss the implementation of a shared UI component library as a solution to promote consistency and streamline development efforts.
   \item Describe how was static assets sharing managent.
\end{itemize}

\section{Routing}
\begin{itemize}
   \item How was the routing issue resolved
   \item Which technologies are utilized for both internal and external routing
\end{itemize}

\section{Cross-application communication}
\begin{itemize}
   \item Discuss when micro-frontends must communicate with each other.
   \item Explain the techniques utilized for communication.
   \item Discuss how was tight coupling avoided.
\end{itemize}

\section{Versoning \& Infrastructure}
\begin{itemize}
   \item Discuss the type of repository employed (Mono-repo/Multi-repos) and reasons behind its selection.
   \item Enumerate all automated workflows which were utilized.
   \item Highlight any additional tools employed
   \item Describe the deployment process
\end{itemize}

\section{Testing}
\begin{itemize}
   \item Detail the types of tests utilized.
   \item  Explain the testing process, including any automation implemented.
   \item List the testing tools utilized.
\end{itemize}